---
title: "R Notebook"
output: html_notebook
---
## Import libraries
```{r}
library(tidymodels)
library(randomForest)
library(caret)
library(e1071)
```

## Import datasets
```{r}
df_other <- Train %>%
            mutate(Label = factor(Label))
df_test  <- Test

# training set proportions by Label
df_other %>% 
  count(Label) %>% 
  mutate(prop = n/sum(n))

```
## Validation set
```{r}
set.seed(234)
val_set <- validation_split(df_other, 
                            strata = Label, 
                            prop = 0.80)
val_set
```

## A First MODEL: TREE-BASED ENSEMBLE
##  Query the number of cores 
```{r}
cores <- parallel::detectCores()
cores
```

## Pass engine-specific arguments
```{r}
rf_mod <- 
  rand_forest(mtry = tune(), min_n = tune(), trees = 1000) %>% 
  set_engine("ranger", num.threads = cores) %>% 
  set_mode("classification")

```

# CREATE THE RECIPE AND WORKFLOW

```{r}
rf_recipe <- 
  recipe(Label ~ ., data = df_other) %>% 
  step_novel(all_nominal(), -all_outcomes())  %>% 
  update_role(ID, new_role = "ID")
   
  
```

## Adding this recipe to our parsnip model gives us a new workflow
```{r}
rf_workflow <- 
  workflow() %>% 
  add_model(rf_mod) %>% 
  add_recipe(rf_recipe)

```

# TRAIN AND TUNE THE MODEL
When we set up our parsnip model, we chose two hyperparameters for tuning:

```{r}
rf_mod
```

## Show what will be tuned
```{r}
extract_parameter_set_dials(rf_mod)
```

We will use a space-filling design to tune, with 25 candidate models:
```{r}
set.seed(345)
rf_res <- 
  rf_workflow %>% 
  tune_grid(val_set,
            grid = 25,
            control = control_grid(save_pred = TRUE),
            metrics = metric_set(roc_auc))

```

Here are our top 5 random forest models, out of the 25 candidates:
```{r}
rf_res %>% 
  show_best(metric = "roc_auc")
```

## Plotting the results of the tuning process 
```{r}
autoplot(rf_res)
```
```{r}
rf_best <- 
  rf_res %>% 
  select_best(metric = "roc_auc")
rf_best
```

## Select the best model according to the ROC AUC metric
```{r}
rf_best <- 
  rf_res %>% 
  select_best(metric = "roc_auc")
rf_best
```
##
```{r}
rf_res %>% 
  collect_predictions()
```
## To filter the predictions for only our best random forest model
```{r}
rf_auc <- 
  rf_res %>% 
  collect_predictions(parameters = rf_best) %>% 
  roc_curve(Label, .pred_1) %>% 
  mutate(model = "Random Forest")

```


# THE LAST FIT
```{r}
# the last model
last_rf_mod <- 
  rand_forest(mtry = 7, min_n = 7, trees = 1000) %>% 
  set_engine("ranger", num.threads = cores, importance = "impurity") %>% 
  set_mode("classification")

# the last workflow
last_rf_workflow <- 
  rf_workflow %>% 
  update_model(last_rf_mod)

splits      <- initial_split(df.train, strata = Label)


# the last fit
set.seed(345)
last_rf_fit <- 
  last_rf_workflow %>% 
  last_fit(splits )

last_rf_fit



```


#  Train the model


Set the control parameter
You will proceed as follow to construct and evaluate the model:

* Evaluate the model with the default setting
* Find the best number of mtry
* Find the best number of maxnodes
* Find the best number of ntrees
* Evaluate the model on the test dataset

## Default setting
K-fold cross validation is controlled by the trainControl() function

# Define the control
```{r}
trControl <- trainControl(method = "cv",
    number = 5,
    search = "grid")
```
Let’s try the build the model with the default values.
```{r}
set.seed(1234)
# Run the model
rf_default <- train(Label~.,
    data = df.train,
    method = "rf",
    metric = "Accuracy",
    trControl = trControl)
# Print the results
print(rf_default)
```

